---
title: "Curriculum Vitae"
author: "Duk Gyoo Kim"
date: "Updated `r format(Sys.time(), '%B %d, %Y')`"
always_allow_html: yes
header-includes:
   - \usepackage{fontawesome5}
   - \usepackage{academicons}   
output:
  bookdown::pdf_document2:
    toc: no
    latex_engine: lualatex    
    keep_tex: yes
  bookdown::html_document2: default
  bookdown::epub_book: default
  bookdown::word_document2: default
---

```{r global_options, include=FALSE, cache=FALSE}
## Set some options for knitr to apply globally
knitr::opts_chunk$set(cache=FALSE,
                      echo=FALSE,
                      autodep=TRUE,
                      message=FALSE,
                      warning=FALSE,
                      dev='tikz',
                      fig.align='center')
## Convert pdf to png for non-latex output since tikz pdf output does
## not appear to work for some browsers (Yihue sent this work-around). Note
## that this requires sudo port install ImageMagick then
## install.packages("magick") (adding density=300 improves image quality
## dramatically and produces html files identical in size to dev='tikz')
##
## NOTE - for non-latex output it appears this is run and not cached,
## so to avoid this overhead, while editing Build Book -> bookdown: pdf_book
## instead of all formats.
knitr::opts_hooks$set(dev = function(options) {
  if(identical(options$dev, 'tikz') && !knitr:::is_latex_output()) {
    options$fig.process = function(x) {
      if (!grepl('[.]pdf$', x)) return(x) 
      x2 = sub('pdf$', 'png', x)
      magick::image_write(magick::image_convert(magick::image_read(x,density=300),colorspace="rgb"),x2,format='png')
      x2
    }
  }
  options
})
```                      

## \faHome\ Contact Information {-}

-   \faPaperPlane\ Department of Economics\
    Kenneth Taylor Hall, Room 402\
    McMaster University\
    1280 Main Street West\
    Hamilton, Ontario, Canada, L8S 4M4

-   [\faEnvelope](mailto:d.kim@mcmaster.ca) d.kim@mcmaster.ca

-   \faPhone\ (905) 519 2558

## \faGlobeAmericas\ Academic Profiles and Website {-}

-   [\faGithub\ GitHub Homepage: kimdukgyoo.github.io](https://kimdukgyoo.github.io) 

-   [\aiGoogleScholar\ Google Scholar Profile: scholar.google.com/citations?user=AdwJwrEAAAAJ](https://scholar.google.com/citations?user=AdwJwrEAAAAJ)

-   [\aiIDEASRePEc\ IDEAS/RePEc Profile: ideas.repec.org/f/pki511.html](https://ideas.repec.org/f/pki511.html)

-   [\aiOrcid\ ORCID Profile: orcid.org/0000-0002-8906-5630](https://orcid.org/0000-0002-8906-5630) 

-   [\aiResearchGate\ ResearchGate Profile: www.researchgate.net/profile/Duk_Gyoo_Kim](https://www.researchgate.net/profile/Duk_Gyoo_Kim) 

## Academic Background {-}

-  \faGraduationCap\ *Education:*

    Ph.D.in Economics (2015), Cornell University, Ithaca, United States\
    M.A.in Economics (2010), Yonsei University, Seoul, South Korea\
    B.A.in Economics (2008), Yonsei University, Seoul, South Korea

-   *Fields of Specialization:*

    Public Economics, Political Economy\
    Experimental Economics

-   *Professional Affiliations:*

    American Economic Association\
    European Economic Association\
    Korean-American Economic Association\
    Econometric Society
    
## Current Positions {-}

-   Assistant Professor, Department of Economics, University of Mannheim (2017-)

-   Visiting Assistant Professor, Department of Economics, McMaster University (2019)


## Past Positions {-}

-   Postdoctoral Scholar, Division of the Humanities and Social Sciences, California Institute of Technology (2015-2017)

## \faAward\ Honours and Awards {-}

-   to be added

## \faBookOpen\ Editorial Positions {-}

-   n.a.

## Visiting Appointments {-}

-   Visiting Researcher, CESifo (2019)

-   Visiting Scholar, Sogang University, Seoul Korea (2016)

## Courses Taught {-}

-   *Graduate:*

    Public Economics
    
-   *Undergraduate:*

    Public Choice


## Grants and Fellowships {-}

1. to be added

1. there are some

## \aiGoogleScholar\ Google Scholar Citation Summary {-}

<center>

```{r,message=FALSE,warning=FALSE,echo=FALSE,results='asis'}
foo <- gcite::gcite_user_info('AdwJwrEAAAAJ',verbose=FALSE)
pander::panderOptions('table.alignment.default',c('left','right','right'))
pander::pander(foo$citation_indices)
```

</center>

```{r,message=FALSE,fig.asp=0.4,out.width="75%",warning=FALSE,echo=FALSE,results='asis'}
require(ggplot2)
require(gridExtra)
require(scholar)
plot1 <- qplot(1)
plot2 <- qplot(1)
## Adjust for discrepancy in total (field All[1] in call to gcite)
adjust <- foo$citation_indices$All[1]-sum(foo$overall_citations$n_citations)
plot1 <- ggplot(foo$overall_citations,aes(x=year,y=n_citations))+
    geom_bar(stat='identity')+
    theme_bw()+
    xlab('Year')+
    ylab('Citations/Year')
plot2 <- ggplot(foo$overall_citations,aes(x=year,y=cumsum(n_citations)+adjust))+
    geom_bar(stat='identity')+
    theme_bw()+
    xlab('Year')+
    ylab('Cumulative Citations')
grid.arrange(plot1, plot2, ncol=2)    
```

## Peer Reviewed Publications {-}

1. to be added

1. there are some

## Work Submitted for Publication {-}

- to be added

<!-- Submitted to JAE May 13 2018, desk reject May 22 2018, submitted to Econometrics Journal Nov 6 2018, mea culpa for delay, returned for formatting (dicks), 45 minutes to get it running -->

- there are some

<!-- Submitted to Journal of Econometrics April 3 2018 -->

## Conference and Seminar Presentations {-}

1. to be added

1. there are some

## Referee and Review Activities {-}

to be added. there are some.