% LaTeX file for resume 
% This file uses the resume document class (res.cls)
\documentclass[margin, letterpaper]{res} 
\usepackage{hyperref}
\usepackage{multicol}
\hypersetup{colorlinks=true, linkcolor=blue,  citecolor=blue, urlcolor=blue} 
\usepackage{inputenc}
\usepackage{fontenc}
\usepackage{fouriernc}
% the margin option causes section titles to appear to the left of body text 
\textwidth=5.3in % increase textwidth to get smaller right margin

\begin{document} 
\name{\Large{Duk Gyoo Kim}\\[12pt]} % the \\[12pt] adds a blank line after name
%\address{467 Uris Hall, Cornell University\\Ithaca, NY 14853 USA}
%\address{Phone: (607) 793-6539\\ E-mail: \href{mailto:dk626@cornell.edu}{dk626@cornell.edu} }

\begin{resume} 
\section{Contact Information} Office: L7, 3-5, Room 225, 68161 Mannheim, Germany\\
Phone: +49-621-181-1797 (Office), +49-157-7482-7036 (Mobile)\\
Email: \href{mailto:d.kim@uni-mannheim.de}{d.kim@uni-mannheim.de}\\
Webpage: \url{https://kimdukgyoo.github.io}

\section{Academic Positions}
\textbf{Assistant Professor}, Department of Economics, University of Mannheim, 2017--\\
\textbf{Postdoctoral Scholar}, California Institute of Technology, 2015--2017\\
(* Dan Searle Fellowship in Economics/ Mentor: Thomas R. Palfrey)

\section{Affiliations}
\textbf{Affiliate Member}, CESifo, Munich, 2020--

\section{Fields}
\textbf{Primary}: Public Economics, Political Economy, Experimental Economics\\
\textbf{Secondary}: Microeconomic Theory, Behavioral Economics

\section{Education} 
\textbf{Ph.D. in Economics,} Cornell University, Aug. 2015\\
(* Fulbright Graduate Study Award/ Advisers: Stephen Coate and Robert H. Frank)\\
\textbf{M.A. in Economics,} Yonsei University, Seoul Korea,  Aug. 2010\\
\textbf{B.A. in Business Administration,} Yonsei University, Seoul Korea, Feb. 2008

\section{Publications}
\begin{enumerate}
\item Multilateral Bargaining with Proposer Selection Contests (with Sang-Hyun Kim), accepted at \emph{Canadian Journal of Economics}
\item Recognition without Replacement in Legislative Bargaining, \emph{Games and Economic Behavior}, 2019, Volume 118, 161--175
\item A Theory of FAQs: Public Announcements with Rational Ignorance (with Yeochang Yoon), \emph{Journal of Economic Behavior \& Organization}, 2019, Volume 158, 560--574
\item Positional Concern and Low Demand for Redistribution of the Poor, \emph{European Journal of Political Economy}, 2019, Volume 56, 27--38
\item Population Uncertainty in Voluntary Contributions of Public Goods, \emph{Journal of Economic Behavior \& Organization}, 2018, Volume 145, 218--231
\item The Second-Tier Trap: Theory and Experimental Evidence, \emph{International Journal of Economic Theory}, 2018, Volume 14, Issue 4, 323--349
\item Response time in choosing the most or least preferred option, \textit{Economics Bulletin}, 2016, Vol. 36 No. 1 pp. 595--600
\end{enumerate}
%\begin{enumerate}
%\item Guide to Effective Retirement Pension Choices: An Experimental Design (with Seura Ha, Sang-Hyun Kim, and Euncheol Shin), \emph{Journal of Financial Regulation and Supervision}, 2019, Vol 6(2), 79--141 (in Korean)
%\item Why Are the Poor Conservative? (with Paul Moon Sub Choi), \textit{The Korean Journal of Economics}, 2015, Vol 22(1), 15--24
%\end{enumerate}

\section{Working Papers}
\begin{enumerate}
\item Multilateral Bargaining over the Division of Losses (with Wooyoung Lim), CESifo Working Paper No. 8011
\item Penalty Lottery
\item Big and Small Lies (with Franziska Heinicke and Diogo Geraldes), CESifo Working Paper No. 8142, Resubmitted to \emph{Journal of Behavioral and Experimental Economics}
\item Clustering Standard Errors at the ``Session'' Level, CESifo Working Paper No. 8386
\item ``One Bite at the Apple'': Legislative Bargaining without Replacement
\item Probability Matching and Strategic Decision Making (with Hee Chun Kim)
\item Collective Proofreading and the Optimal Voting Rule (with Jinhyuk Lee and Euncheol Shin)
\end{enumerate}

\section{Work in Progress}
\begin{enumerate}
\item Paradoxes of Network in Bargaining (with Joosung Lee)
%\item Political Blurring over Non-linear Tax Schedules (with Felix Bierbrauer)
\item Distributive Politics on Public Bads (with Andrzej Baranski-Madrigal)
\item Viable Nash Equilibria: An Experiment (with Daehong Min and John Wooders)
\end{enumerate}

\section{Fellowships, Grants, Honors, and Awards}
\begin{itemize}
\item University of Mannheim, SFB 884 ``The political economy of reforms" (financed by German Research Foundation), Project A7 (2018--2021, with Hans Peter Gr{\"u}ner).
\item Dan Searle Postdoctoral Fellowship in Economics, Oct. 2015--Sept. 2017.
\item East Asia Program Research Travel Grant, May 2015.
\item Einaudi Center International Research Travel Award, Mar. 2015.
\item Charles Koch Foundation Dissertation Research Grant, 2014--2015
\item The Howard and Abby Milstein Graduate Teaching Award, 2014.
\item Cornell Graduate School Research Travel Grant, Nov. 2014.
\item Hayek Fund for Scholars, The Institute of Humane Studies, 2014, 2015, 2016, 2017.
\item The Institute of Humane Studies Conference and Research Grant, Sept. 2014.
\item Cornell Population Center Rapid Grant, 2014, 2015.
\item Cornell Graduate School Conference Travel Grant, 2013, 2014.
\item Science of Philanthropy Initiative PhD grant, Mar. 2014
\item Fulbright Graduate Study Award, Aug. 2010--Jul. 2012
%\item Brain Korea 21 Research Assistantship, Ministry of Education, South Korea, August 2008 to February 2010
%\item Citi-KIF (Korean Institute of Finance) financial research paper competition grant (\$3,500), June 2009
%\item Citi-KAIST financial research paper competition grant (\$3,000), March 2008
%\item \textit{Maeil} Business and Economy Newspaper 22nd Economic Thesis Award, October 2007
%\item Provost's Honor, UC San Diego (Exchange Program), Fall 2006 quarter 
%\item Dean's Honor of Distinguished Students, Yonsei University, Spring 2005, and Fall 2005 
\end{itemize}

\section{Conference/ Seminar Presentations (Last five years)}
\textbf{2020}: HeiKaMaxY Workshop, Mannheim/ZEW Experimental seminar, Reading Experimental and Behavioral Economics Workshop, Econometric Society World Congress, Korean Economic Review International Conference, Yonsei University, ESA Global Around-the-Clock Virtual Conference, Econometric Society Winter Meeting\\% (*scheduled)
\textbf{2019}: Asia-Pacific Economic Science Association Meeting, New York University Abu Dhabi, University of Mannheim, HeiKaMaX Workshop, Max Planck Institute for Tax Law and Public Finance, International Meeting on Experimental and Behavioral Social Sciences, North American Summer Meeting of the Econometric Society, Economics Science Association World Meeting, Korean Economic Review International Conference, University of British Columbia, University of Victoria, University of Massachusetts Amherst, Queen's University, Carleton University, Concordia University, Canadian Public Economics Group Conference, McMaster University, Florida State University, Southern Economic Association Meeting, University of Toronto, University of Western Ontario, University of Guelph, Bilkent University\\
\textbf{2018}: Royal Economic Society Conference, HeiKaMaX Workshop, Social Choice and Welfare Conference, Yonsei University, Asian Meeting of the Econometric Society, Foundations of Risk and Uncertainty Conference, Economic Science Association World Meeting, Stony Brook International Conference on Game Theory, European Association of Law and Economics Conference, Nordic Conference on Behavioral and Experimental Economics, HKUST Experimental Workshop, Edinburgh Business School, HeiKaMaxY Workshop\\
\textbf{2017}: Max Planck Institute for Tax Law and Public Finance, University of Mannheim, Korea Informational Society Development Institute, Korea Institute of Public Finance, Korea Institute of International Economic Policy, Korea Energy Economics Institute, University of Massachusetts Amherst, Western Political Science Association Conference, Kyung Hee University, SKKU Junior Faculty Research Conference, North American Meeting of the Econometric Society, Western Economics Association International Annual Meetings, Yonsei Young Economists Workshop, KAEA-KIPF Conference, Yonsei University, Midwest Economic Theory Conference, HeiKaMaxY Workshop\\
\textbf{2016}: Chapman University, Southwest Experimental and Behavioral Economics Workshop Annual Conference, Canadian Economics Association Annual Conference, Caltech, Western Economics Association International Annual Meetings, Sogang University, Seoul National University, KDI School of Public Policy and Management, KAEA-KEA International Conference, Cornell University, Canadian Public Economics Group Conference, North-American ESA Conference, Sonoma State University, Midwest Economic Theory Conference%\\
%\textbf{2015}: The 52nd Annual Meetings of the Public Choice Society, The 85th Annual Conference of the Southern Economic Association\\
%\textbf{2014}: Canadian Economics Association Annual Conference, The Institute of Humane Studies Summer Research Colloquium, KAEA-KEA International Conference, The 9th Economics Graduate Student Conference at Washington University in St. Louis, Canadian Public Economics Group Conference, The 2nd Science of Philanthropy Initiative Conference

\section{Other Activities}
\begin{itemize}
\item Referee service: Economic Journal, Journal of Public Economics, European Economic Review, International Journal of Game Theory, Economics E-Journal, PLOS ONE, Canadian Journal of Economics, Journal of Economic Behavior and Organization, European Journal of Political Economy, Journal of the Economic Science Association
%\item Departmental service: Junior recruiting committee, University of Mannheim, 2017--2018
\item CES Visiting Scholar, Ludwig Maximilian University of Munich, Dec 2019
\item Visiting Scholar, Department of Economics, McMaster University, Fall 2019
\item Short Visits: School of Economics, Sogang University, Korea, July 2016
\end{itemize}

\section{Citizenship} South Korea (EU Blue Card)% (J-1 Visa)%South Korea (F-1 Visa since 2012, J-1 from 2010 to 2012)

\section{Affiliations} American Economic Association, European Economics Association, Econometric Society, Korean-American Economic Association

\section{Languages} Korean(native), English(fluent)

\section{References} \textbf{Thomas R. Palfrey} \href{mailto:trp@hss.caltech.edu}{trp@hss.caltech.edu}\\
Flintridge Foundation Professor of Economics and Political Science, Caltech\\\\
\textbf{Stephen Coate} \href{mailto:sc163@cornell.edu}{sc163@cornell.edu}\\
Kiplinger Professor of Public Policy, Cornell University\\\\
%\textbf{Robert H. Frank} \href{mailto:rhf3@cornell.edu}{rhf3@cornell.edu}\\
%Henrietta Johnson Louis Professor of Management and Professor of Economics\\
%Johnson Graduate School of Management, Cornell University\\\\
\textbf{Hans Peter Gr\"{u}ner} \href{mailto:hgruener@staffmail.uni-mannheim.de}{hgruener@staffmail.uni-mannheim.de}\\
Professor of Economics, University of Mannheim\\\\
\textbf{Wooyoung Lim} \href{mailto:wooyoung@ust.hk}{wooyoung@ust.hk}\\
Associate Professor of Economics, Hong Kong University of Science and Technology
\begin{flushright}
Last Updated: \today
\end{flushright}
\end{resume} 
\end{document} 